\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\setlength{\footskip}{5pt}

\usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Aman Goyal} \\ \vspace{2pt}
    \small +91 9520409003 $|$
    \href{mailto:amangoyel0@gmail.com}{\underline{amangoyel0@gmail.com}} $|$
    \href{https://agoyel25.github.io}{\underline{Portfolio}} $|$
    \href{https://www.linkedin.com/in/amangoyal25}{\underline{LinkedIn}} $|$
    \href{https://github.com/agoyel25}{\underline{GitHub}}
\end{center}

\section{Summary}
\resumeItemListStart
\resumeItem{Backend \& Infrastructure Engineer with 2 years building production systems on AWS and shipping AI-native products --- from cloud infrastructure and distributed job pipelines to browser-based agents that operate within live software environments.}
\resumeItem{Strong in Infrastructure as Code (Terraform), containerization (Docker), and CI/CD automation (GitHub Actions, GitLab CI) with a focus on reliability, self-healing architecture, and zero-downtime deployments.}
\resumeItem{Backend experience across Python, TypeScript, and Golang --- building job pipelines, REST APIs, subscription systems, and internal microservices in production environments.}
\resumeItem{Built AI-integrated products across multiple layers: browser-native agents that inject into and extract state from live software interfaces; semantic search and retrieval systems using embeddings; async AI generation pipelines using fal.ai, Replicate, and Remotion.}
\resumeItem{Shipped real products with measurable outcomes: 2,500+ users, \$20K+ cumulative revenue, 99.9\% uptime, and 1,000+ videos processed.}
\resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Dehradun, Uttarakhand}
      {MCA (Aug. 2022 -- July 2024) \quad B.Sc. Information Technology (Aug. 2019 -- July 2022)}{}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Early Engineer \#3 --- DevOps \& Backend}{Nov. 2024 -- Mar. 2026}
{Vubo (vubo.ai)}{Remote}
\resumeItemListStart
\resumeItem{Contributed to a platform serving 2,500+ users and \$20K+ in cumulative revenue, owning infrastructure, backend services, and AI integration end-to-end.}
\resumeItem{Architected and operated highly available AWS infrastructure (ECS Fargate, EC2, VPC, IAM, S3, RDS, Lambda, CloudFront) with self-healing design maintaining 99.9\% uptime.}
\resumeItem{Provisioned all infrastructure via Terraform (IaC) with modular, environment-consistent architecture across dev, staging, and production.}
\resumeItem{Engineered CI/CD pipelines using GitHub Actions with full automation across dev, staging, and prod; integrated AWS CodeDeploy for automated rollback, reducing failed release impact to negligible levels.}
\resumeItem{Built and maintained backend services in TypeScript (Next.js) and Golang --- including subscription-gated access, atomic credit deduction, rate limiting, and a referral growth system; backed by PostgreSQL and Redis.}
\resumeItem{Developed Golang microservices for internal tooling: admin dashboard, automated database backups, and free-tier utilities (background remover, etc.).}
\resumeItem{Integrated AI video generation pipeline using fal.ai, Replicate, and Remotion; orchestrated async API calls via Inngest with prompt engineering to ensure consistent video output quality across 1,000+ processed videos.}
\resumeItem{Deployed observability stack using OpenTelemetry, Prometheus, and structured logging --- reducing mean time to debug incidents by \textasciitilde60\%.}
\resumeItem{Optimized CloudFront CDN caching strategies, cutting average asset latency by \textasciitilde35\% globally.}
\resumeItem{Cut monthly infrastructure spend by \textasciitilde40\% through autoscaling tuning, storage optimization, and compute right-sizing.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer --- DevOps \& Backend (Freelance)}{Jun. 2024 -- Jan. 2025}
{Independent Consulting}{Remote}
\resumeItemListStart
\resumeItem{Delivered end-to-end AWS infrastructure for startup clients using Terraform, Docker, and CI/CD pipelines (GitHub Actions, GitLab CI).}
\resumeItem{Configured Linux servers with hardened networking, reverse proxy setup (Caddy/Nginx), TLS termination, and VPN-restricted access for secure production environments.}
\resumeItem{Automated infrastructure provisioning and configuration management workflows using Python, Shell, and Ansible.}
\resumeItem{Established monitoring and logging stacks (Prometheus, Grafana, ELK) for real-time observability and alerting across client systems.}
\resumeItem{Reduced client SaaS tooling costs significantly by migrating to self-hosted observability and support tools while maintaining reliability.}
\resumeItem{Enforced security best practices, including VPC isolation, IAM least-privilege policies, HTTPS/TLS, and distributed systems resilience patterns.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Vubo} $|$ \emph{AI Video Generation SaaS --- Next.js, Golang, AWS, Remotion, fal.ai}}{\href{https://vubo.ai}{vubo.ai}}
\resumeItemListStart
\resumeItem{Full-stack AI SaaS platform for automated video generation serving 2,500+ users with \$20K+ in cumulative revenue.}
\resumeItem{Orchestrated async AI video pipeline using fal.ai, Replicate, and Remotion; applied prompt engineering techniques to improve generation consistency and output quality.}
\resumeItem{Developed distributed background job system using Inngest and BullMQ for media processing, credit management, and workflow orchestration at scale.}
\resumeItem{Shipped backend features in TypeScript and Golang: subscription logic, atomic credit deduction, rate limiting, referral system, and internal admin tooling; leveraged PostgreSQL (RDS) and Redis (ElastiCache) for data and caching layers.}
\resumeItem{Integrated OpenTelemetry tracing and PostHog analytics; optimized CI/CD with GitHub Actions caching and automated CloudFront invalidations.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Lazyapply.xyz} $|$ \emph{AI Reply Assistant --- Astro, Cloudflare, OpenRouter}}{\href{https://lazyapply.xyz}{lazyapply.xyz}}
\resumeItemListStart
\resumeItem{Browser-native agent that injects into and operates within live software interfaces (X, Reddit) --- extracting structured DOM state, augmenting with stored user context, and generating AI output inside the host application without modifying it.}
\resumeItem{Engineered real-time DOM scraping using MutationObserver to extract composer state and tweet thread context; fed extracted data into dynamic prompt construction for OpenRouter-powered LLM calls.}
\resumeItem{Applied context engineering techniques to improve reply relevance and match user tone across different conversation types.}
\resumeItem{Backend powered by Cloudflare D1 (SQL), KV storage, and edge functions for low-latency stateless execution globally.}
\resumeItem{Frontend built with Astro for minimal client-side overhead and fast load performance.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{BookmarkBrain} $|$ \emph{Local-First AI Knowledge Base --- TypeScript, Chrome Extension, Embeddings}}{\href{https://github.com/agoyel25/BookmarkBrain}{github.com/agoyel25/BookmarkBrain}}
\resumeItemListStart
\resumeItem{Open-source Chrome extension with 50 active users; turns X and Reddit bookmarks into a queryable semantic knowledge base entirely in-browser.}
\resumeItem{Built local-first storage architecture with semantic embeddings and vector retrieval --- zero backend dependency, all personal data stays on-device.}
\resumeItem{Implemented BYOK abstraction layer supporting OpenAI, OpenRouter, and Gemini; natural language Q\&A returns answers with citations back to source posts.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Cloud Infrastructure Automation} $|$ \emph{AWS, Terraform, CI/CD, Kubernetes (EKS)}}{}
\resumeItemListStart
\resumeItem{Provisioned modular AWS infrastructure using Terraform (VPC, ECS, EKS, RDS, ALB, CloudFront, WAF, ElastiCache).}
\resumeItem{Configured CI/CD pipelines with GitHub Actions covering automated deployments, artifact management, and rollback mechanisms.}
\resumeItem{Implemented blue-green deployment strategy and autoscaling policies for high availability and zero-downtime releases.}
\resumeItem{Set up CloudWatch monitoring and custom metrics pipelines for proactive incident detection and alerting.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages:} Python, TypeScript, JavaScript, Golang, SQL, Shell \\
\textbf{Cloud \& DevOps:} AWS (EC2, ECS, EKS, S3, CloudFront, RDS, Lambda, IAM, VPC), Terraform, Docker, Kubernetes (EKS), CI/CD \\
\textbf{CI/CD \& Automation:} GitHub Actions, GitLab CI, AWS CodeDeploy, Ansible, Infrastructure as Code (IaC) \\
\textbf{Monitoring \& Observability:} Prometheus, Grafana, ELK, OpenTelemetry, CloudWatch, Logging \& Alerting \\
\textbf{Backend \& Systems:} REST APIs, Distributed Systems, Microservices, Linux, Networking, Reverse Proxy \\
\textbf{AI \& Integrations:} LLM APIs (OpenAI, Gemini, Mistral, OpenRouter), Semantic Embeddings, Vector Retrieval, Browser Extension APIs, fal.ai, Replicate, Remotion, Inngest, Prompt Engineering \\
\textbf{Databases:} PostgreSQL, Redis, Cloudflare D1, KV Storage \\
\textbf{Other:} Performance Optimization, Cost Optimization, System Design
}}
\end{itemize}

\end{document}